# Rotation Matrice Example

## Getting Started


Lets start by creating an empty script Start with the basic cleaning commands
```{r eval=FALSE}
clear; 
```


`clear` deletes all of the variables in your workspace - this makes sure that every time we run our code, we're always using the data from this run of the script, and not a previous run.`

```{r eval=FALSE}
clc; 
```

`clc` deletes all of the old messages in the console or command window. This makes sure that the only messages we see on our command window come from this run of the script, and not from a previous run.

```{r eval=FALSE}
close all; 
```
`close all` closes all of the previous plots and graph windows.  This way you know that the plots you see generated are new, and not old data.

Let's load up our aircraft into Matlab

```{r eval=FALSE}
load Lab_Airplane.mat
```

Take a look at the new variables in your workspace

```{r eval=FALSE}
who -file Lab_Airplane.mat
```

The `who` command prints a list of variables - in this case, we've asked it about the airplane_model file

    Your variables are: 
    
    airplane f
    
## Making an Airplane

Lets take a closer look at the `airplane` variable

```{r eval=FALSE}
size(airplane)
```

    ans = 1x2
        36    3
        
Airplane is a 36 row by 3 column matrix. This variable represents the x, y, and z coordinates of every corner in our airplane model.  There are 36 points within our airplane model.

```{r eval=FALSE}
airplane(1,:)
```

    ans = 1x3
    
        - 6.8000    0.5000    0.8000
        
The first point in our model occurs at the 3D point: -6.8 on the x-axis, 0.5 on the y-axis and 0.8 on the z-axis.

Let's plot this